---
title: "Final Project"
author: "Sanyukta Ghai"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true    
    toc_depth: 2    
    toc_float: TRUE
---

```{r echo = FALSE}
# Course: BUAN 5210
# Title: Quick Project 1 Technical Appendix
# Purpose: Analyzing office sales data 
# Date: Jan 26, 2019
# Author: Nancy Jain and Sanyukta Ghai
```


Clear environment
=================

```{r, warning= FALSE, message= FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```


Load packages 
==============

```{r, warning= FALSE, message= FALSE }
# Load libraries
library(tidyverse)
library(ggplot2)
library(corrplot)
```


Load data
=========================================
This dataset contains a list of video games with sales greater than 100,000 copies and is obtained from kaggle.com. It represents video games sales from a website vgchartz.com from 1980 to 2016.

```{r}
#Load Data
video_games_raw_data <- read.csv("../raw_data/vgsales.csv")

str(video_games_raw_data)

summary(video_games_raw_data)

```
### Observations

+ Table contains 16598 observations of 11 variables  
+ 5 factor variables - Name, Platform, Year, Genre, Publisher  
+ 6 numeric variables - Rank, NA_Sales, EU_Sales, JP_Sales, Other_Sales, Global_Sales

### Filter data based on our scope

```{r}
# Years from 2000 onwards
# Remove Rank column
# Consider only US Sales  
# Remove rows with 0 sales
video_games_data <- video_games_raw_data %>%
  select(-c(Rank, EU_Sales, JP_Sales, Other_Sales, Global_Sales)) %>%
  filter(Year %in% seq(2000, 2016, by = 1)) %>%
  mutate(Year = Year %>% droplevels()) %>%
  filter(NA_Sales > 0.000)

str(video_games_data)

summary(video_games_data)

```

### Observations

+ 5 factor variables - Name, Platform, Year, Genre, Publisher  
+ 1 numeric variable - NA_Sales


Questions to be answered
========================
Company A want to know the feasibility of an online game streaming platform similar to ‘Netflix’ for games. They would like to know how to design their initial portfolio on the platform to generate maximum revenue.  

+ Should Company A tie up with a single publisher or platform?  
+ Which 3 top performing games should they include in their portfolio  
+ How should their portfolio split be in terms of game genres


# I) Practical Analysis

1. Univariate non-graphical -- Categorical
===========================================

Categorical data - tabulation


2. Univariate graphical -- Categorical
===========================================

Histograms


3. Univariate non-graphical -- Quantitative
============================================

Descriptive Statistics


4. Univariate graphical -- Quantitative
=========================================

Histograms


Boxplots


5. Multivariate non-graphical -- Categorical
============================================

Cross-Tabs


Proportion Cross-Tabs


6. Multivariate graphical code -- Categorical
==============================================

Grouped Summary graphs with more than 1 Categorical variables



7. Multivariate non-graphical -- Quantitative
==============================================

Correlation plots


8. Multivariate graphical code -- Quantitative
===============================================

Pairwise Plot



9. Multivariate non-graphical -- Categorical and Quantitative
=============================================================

matrix tables


10. Multivariate graphical -- Categorical and Quantitative
=============================================================

matrix group by and summarize quant graphs


# II) Statistical Analysis


Questions for statistical analysis
=========================================



Multiple Linear regression
================================

Summary
=======


Save Image of file
===================

```{r, warning= FALSE, message= FALSE }

# Save the rds file to reuse anything from this file in another file
save.image("TA.RData")
# recover using load()
# load("TA.RData")

```





