---
title: "Final Project"
author: "Sanyukta Ghai"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true    
    toc_depth: 2    
    toc_float: TRUE
---

```{r echo = FALSE}
# Course: BUAN 5210
# Title: Quick Project 1 Technical Appendix
# Purpose: Analyzing office sales data 
# Date: Jan 26, 2019
# Author: Nancy Jain and Sanyukta Ghai
```


Clear environment
=================

```{r, warning= FALSE, message= FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```


Load packages 
==============

```{r, warning= FALSE, message= FALSE }
# Load libraries
library(tidyverse)
library(ggplot2)
library(corrplot)
```


Load data
=========================================

```{r}

```


Questions to be answered
========================




# I) Practical Analysis

1. Univariate non-graphical -- Categorical
===========================================

Categorical data - tabulation


2. Univariate graphical -- Categorical
===========================================

Histograms


3. Univariate non-graphical -- Quantitative
============================================

Descriptive Statistics


4. Univariate graphical -- Quantitative
=========================================

Histograms


Boxplots


5. Multivariate non-graphical -- Categorical
============================================

Cross-Tabs


Proportion Cross-Tabs


6. Multivariate graphical code -- Categorical
==============================================

Grouped Summary graphs with more than 1 Categorical variables



7. Multivariate non-graphical -- Quantitative
==============================================

Correlation plots


8. Multivariate graphical code -- Quantitative
===============================================

Pairwise Plot



9. Multivariate non-graphical -- Categorical and Quantitative
=============================================================

matrix tables


10. Multivariate graphical -- Categorical and Quantitative
=============================================================

matrix group by and summarize quant graphs


# II) Statistical Analysis


Questions for statistical analysis
=========================================



Multiple Linear regression
================================

Summary
=======


Save Image of file
===================

```{r, warning= FALSE, message= FALSE }

# Save the rds file to reuse anything from this file in another file
save.image("TA.RData")
# recover using load()
# load("TA.RData")

```





