---
title: "Final Project"
author: "Sanyukta Ghai"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true    
    toc_depth: 2    
    toc_float: TRUE
---

```{r echo = FALSE}
# Course: BUAN 5210
# Title: Quick Project 1 Technical Appendix
# Purpose: Analyzing office sales data 
# Date: Jan 26, 2019
# Author: Nancy Jain and Sanyukta Ghai
```


Clear environment
=================

```{r, warning= FALSE, message= FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```


Load packages 
==============

```{r, warning= FALSE, message= FALSE }
# Load libraries
library(tidyverse) # tidyverse syntax
library(ggplot2) # Neat Graphs 
library(kableExtra) # Pretty HTML Tables
library(corrplot) # Pairwise correlation plot
library(GGally)  # For ggpairs, a detailed correlation graphic
library(gridExtra) # Arrange graphs in a grid
library(janitor) # Pretty cross-tabs
```


Load data
=========================================
This dataset contains a list of video games with sales greater than 100,000 copies and is obtained from kaggle.com. It represents video games sales from a website vgchartz.com from 1980 to 2016.

```{r}
#Load Data
video_games_raw_data <- read.csv("../raw_data/vgsales.csv")

str(video_games_raw_data)

summary(video_games_raw_data)

```
### Observations

+ Table contains 16598 observations of 11 variables  
+ 5 factor variables - Name, Platform, Year, Genre, Publisher  
+ 6 numeric variables - Rank, NA_Sales, EU_Sales, JP_Sales, Other_Sales

### Filter data based on our scope

```{r}
# Years from 2006 onwards
# Remove Rank column
# Consider only US Sales  
# Remove rows with 0 sales
# Pick top 200 games
video_games_data <- video_games_raw_data %>%
  select(-c(Rank, EU_Sales, JP_Sales, Other_Sales)) %>%
  filter(Year %in% seq(2006, 2016, by = 1)) %>%
  mutate(Year = Year %>% droplevels()) %>%
  filter(NA_Sales > 0.000) %>%
  filter(!Publisher %in% c("NA", "N/A", "Unknown")) %>%
  top_n(200, NA_Sales) %>%
  mutate(Year = Year %>% droplevels()) %>%
  mutate(Platform = Platform %>% droplevels()) %>%
  mutate(Name = Name %>% droplevels()) %>%
  mutate(Publisher = Publisher %>% droplevels()) %>%
  mutate(Genre = Genre %>% droplevels())
  
str(video_games_data)

summary(video_games_data)

```

### Observations

+ 5 factor variables - Name, Platform, Year, Genre, Publisher  
+ 1 numeric variable - NA_Sales


Questions to be answered
========================
Company A want to know the feasibility of an online game streaming platform similar to ‘Netflix’ for games. They would like to know how to design their initial portfolio on the platform to generate maximum revenue.  

+ Should Company A tie up with a single publisher or platform?  
+ Which 3 top performing games should they include in their portfolio  
+ How should their portfolio split be in terms of game genres

Functions
==========

```{r, warning= FALSE, message= FALSE }
# Function to get the relevant grouped data frames
# df -> dataframe
# groupVariable -> the group by column 
# output -> the resulting data frame
getGroupedUnivariateData <- function(df, groupVariable) {
  # group_by() store
  # summarise() reduces variable to descriptive stat
  # count is the new variable name, n() is a counting function
  # percent is a new variable, sum() and nrow() are functions
  # tot_sales_units -> total number of units sold per store
  # tot_revenue -> total revenue per store
  # order_by() tot_revenue and tot_sales_units
  result <- df %>%             
    group_by_(groupVariable) %>%     
    summarise(count = n(),   
              percent = (sum(count) / nrow(df)) * 100, 
              tot_revenue = sum(NA_Sales),   
              avg_revenue = (mean(NA_Sales))) %>%
    arrange(desc(tot_revenue)) %>%
    as.data.frame() 
  
  return(result)
}

# Function to draw histograms using grid.arrange so can see all quant variables together group by variable x
# df -> dataframe
# x -> the group by column 
getGroupedUnivariateHistograms <- function(df, x, flip = TRUE) {
  grid.arrange(
    df %>% 
      ggplot(aes(x = get(x), y = count)) +  
        geom_bar(stat = "identity") + 
        {if(flip)coord_flip()} +
        xlab(x),
    df %>% 
      ggplot(aes(x = get(x), y = tot_revenue)) +
        geom_bar(stat = "identity") + 
        {if(flip)coord_flip()} +
        xlab(x),
    df %>% 
      ggplot(aes(x = get(x), y = avg_revenue)) +
        geom_bar(stat = "identity") + 
        {if(flip)coord_flip()} +
        xlab(x),
    ncol = 2
  )
}

# Function to draw multivariate graphs
# df -> dataframe
# groupVariable1, groupVariable2 -> the group by columns
# output -> no output -> draws the required graph
getMultivariateGraphical <- function(df, groupVariable1, groupVariable2, flipLabel){
  df %>%
    group_by_(groupVariable1, groupVariable2) %>% 
    summarise(count = n()) %>% 
    ggplot(aes(get(groupVariable1), get(groupVariable2))) + 
    coord_flip() +
    geom_tile(aes(fill = -count)) +
    xlab(groupVariable1) +
    ylab(groupVariable2) +
    {if(flipLabel)theme(axis.text.x = element_text(angle = 45))} 
}

```

# I) Practical Analysis

1. Univariate non-graphical -- Categorical
===========================================

Categorical data - tabulation

### Platform

```{r, warning= FALSE, message= FALSE}
# Count and revenue by Platform
vg_platform <- getGroupedUnivariateData(video_games_data, "Platform")
vg_platform %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  scroll_box(height = "300px")
```
### Observations

+ Top 5 Platforms by Total Revenue are X360, Wii, PS3, DS, XOne
+ Maximum number of games on X360(69) and PS3(37)  
+ X360, Wii and PS3 make up to 70% of the total games

### Year

```{r, warning= FALSE, message= FALSE}
# Count and revenue by Year
vg_year <- getGroupedUnivariateData(video_games_data, "Year")
vg_year %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  scroll_box(height = "300px")
```
### Observations

+ Top Years by Revenue are 2010, 2009, 2006
+ Maximum number of games launched between 2007 to 2011

### Genre

```{r, warning= FALSE, message= FALSE}
# Count and revenue by Genre
vg_genre <- getGroupedUnivariateData(video_games_data, "Genre")
vg_genre %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  scroll_box(height = "300px")
```
### Observations

+ Top 3 Genres are Shooter, Sports, Action
+ The top 3 Genres have more than 60% of the total games

### Publisher 

```{r, warning= FALSE, message= FALSE}
# Count and revenue by Publisher
vg_publisher <- getGroupedUnivariateData(video_games_data, "Publisher")
vg_publisher %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  scroll_box(height = "300px")
```
### Observations

+ Top 5 Publishers are Nintendo, Activision, Microsoft Game Studios, Electronic Arts, Take-Two Interactive   
+ Nintendo and Activision have highest total revenue  
+ Nintendo has maximum average revenue followed by Activision and Microsoft Game Studios


2. Univariate graphical -- Categorical
===========================================

Histograms

### Platform

```{r, warning= FALSE, message= FALSE }

# Revenue by Platform
getGroupedUnivariateHistograms(vg_platform, "Platform")

```

### Observations

+ X360 has maximum games  
+ X360 has maximum total revenue  
+ Wii has maximum average revenue

### Year

```{r, warning= FALSE, message= FALSE }

# Revenue by Year
getGroupedUnivariateHistograms(vg_year, "Year")

```

### Observations

+ Most games were released between 2006 to 2011 with 2010 being maximum  
+ Total Revenue is maximum in year 2010
+ Maximum average revenue was in 2006


### Genre

```{r, warning= FALSE, message= FALSE }

# Revenue by Genre
getGroupedUnivariateHistograms(vg_genre, "Genre")

```
### Observations

+ Action & Shooter Genre have the most number of games  
+ Shooter Genre has maximum total revenue   
+ Racing Genre has maximum average revenue


### Publisher

```{r, warning= FALSE, message= FALSE }

# Revenue by Publisher
getGroupedUnivariateHistograms(vg_publisher, "Publisher")

```

### Observations

+ Nintendo followed by Activision in total games and revenue  
+ Nintendo followed by Microsoft Game Studios in average revenue


3. Univariate non-graphical -- Quantitative
============================================

Descriptive Statistics

```{r, warning=FALSE, message=FALSE}

# Get descriptive stats 
summary(video_games_data)

```

### Observations

+ Mean NA_Sales Revenue is 3.8 Millions  
+ Median NA_Sales is 2.65 Millions  
+ Therefore, the distribution is left skewed  
+ Maximum NA_Sales in 41.49 Million  
+ Global_Sales ranges from 2 Million to 82 Million  
+ Mean Global_Sales is 7.3 Million. Median is 5.05 Million. So, left skewed.


4. Univariate graphical -- Quantitative
=========================================

Histograms

```{r, warning=FALSE, message=FALSE}
# Code histograms using ggplot() 
video_games_data %>% 
  ggplot(aes(NA_Sales)) +
  geom_histogram()

video_games_data %>% 
  ggplot(aes(NA_Sales)) +
  geom_histogram() +
  xlim(0,15)
```

### Observations

+ Most NA_Sales between 2 to 10 Million Dollars  
+ Few outliers around 40 Million Dollars

```{r}
# Code histograms using ggplot() 
video_games_data %>% 
  ggplot(aes(Global_Sales)) +
  geom_histogram()

```

### Observations

+ Most Global_Sales between 2 to 40 Million Dollars  
+ Few outliers around 82 Million Dollars



Boxplots

```{r, warning=FALSE, message=FALSE}
# Code boxplot
boxplot(video_games_data$NA_Sales, main = "NA_Sales(Millions")

```

### Observations same as histograms

```{r}
# Code boxplot
boxplot(video_games_data$Global_Sales, main = "Global_Sales(Millions")

```

### Observations

+ Most Global_Sales between 2 to 15 Million Dollars  
+ Few outliers from 15 to 82 Million Dollars

5. Multivariate non-graphical -- Categorical
============================================

Cross-Tabs

```{r, warning= FALSE, message= FALSE }

# Make cross-tabs between two categorical variables using janitor package
video_games_data %>% 
  tabyl(Platform, Publisher) %>% 
  adorn_totals(where = c("row", "col")) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))# %>%
  #scroll_box(height = "300px")

```

### Observations

+ Nintendo has most games for their own platform DS and few games for Wii  
+ Activision and Electronic Arts create games for all platforms  


```{r, warning= FALSE, message= FALSE }

video_games_data %>% 
  tabyl(Publisher, Genre) %>% 
  adorn_totals(where = c("row", "col")) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover")) #%>%
  #scroll_box(height = "300px")
```

### Observations

+ Activision has the most shooter games (22)  
+ Take-Two Interactive and Ubisoft have the most action games (9)  
+ Electronic Arts have the most Sports games (16) 

```{r, warning= FALSE, message= FALSE }

video_games_data %>% 
  tabyl(Genre, Platform) %>% 
  adorn_totals(where = c("row", "col")) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover")) #%>%
  #scroll_box(height = "300px")
```

### Observations

+ X360 has the most shooter games (22)  
+ X360 and PS3 have the most action games (16, 15)  
+ X360 has the most Sports games (11)  


Proportion Cross-Tabs


```{r, warning= FALSE, message= FALSE }

# Make cross-tabs between two categorical variables using janitor package
video_games_data %>% 
  tabyl(Platform, Publisher) %>% 
  adorn_totals(where = c("row", "col")) %>%
  adorn_percentages() %>%
  adorn_pct_formatting() %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))# %>%
  #scroll_box(height = "300px")

```

### Observations

+ Activision in the only Publisher for PC  
+ Sony Computer Entertainment is the only publisher for PSP  
+ Nintendo is the only publisher for WiiU


```{r, warning= FALSE, message= FALSE }

video_games_data %>% 
  tabyl(Publisher, Genre) %>% 
  adorn_totals(where = c("row", "col")) %>%
  adorn_percentages() %>%
  adorn_pct_formatting() %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover")) #%>%
  #scroll_box(height = "300px")
```

### Observations

+ Eidos Interactive, Konami Digital Entertainment, LucasArts, Sony Computer Entertainment Europe, THQ only develop for Action Genre  
+ Mindscape, MTV Games, RedOctane only develop for Misc genre  
+ Bethesda Softworks only develops role-playing genre  
+ Shooter and Action genre have maximum games (22% each)
 

```{r, warning= FALSE, message= FALSE }

video_games_data %>% 
  tabyl(Genre, Platform) %>% 
  adorn_totals(where = c("row", "col")) %>%
  adorn_percentages() %>%
  adorn_pct_formatting() %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover")) #%>%
  #scroll_box(height = "300px")
```

### Observations

+ Strategy games are only played on PC  
+ X360 has a good spread (34.5%) across genres except Platform, Stimulation and Strategy  
+ X360 has maximum share of Shooter, Racing, Sports and Action. X360 is followed by PS3 in the same categories.

6. Multivariate graphical code -- Categorical
==============================================

Grouped Summary graphs with more than 1 Categorical variables


```{r, warning= FALSE, message= FALSE }

getMultivariateGraphical(video_games_data, "Publisher", "Platform", FALSE)

```

### Observations

+ Most publishers developing games for PS3 and X360 Platforms  
+ Microsoft Game Studios develops exclusively for X360 and XOne  
+ Sony Computer Entertainment develops exclusively for PS2, PS3, PS4 and PSP  
+ Nintendo develops exclusively for 3DS, DS, Wii and WiiU  
+ Activision, Electronic Arts develop for almost all platforms  
+ Most others develop for PS and X360 platforms  
+ Need to add more information on platform owners


```{r, warning= FALSE, message= FALSE }

getMultivariateGraphical(video_games_data, "Publisher", "Genre", TRUE)

```

### Observations

+ Activision, Microsoft Game Studios and Electronic Arts leading in Shooter games 
+ Ubisoft, Take-Two Interactive and Sony Computer Entertainment leading in Action games  
+ Nintendo publishes games across the board except Strategy and Adventure


```{r, warning= FALSE, message= FALSE }

getMultivariateGraphical(video_games_data, "Genre", "Platform", FALSE)

```

### Observations

+ Shooter more than Action games on X360 followed by Role-playing and Sports  
+ Action more than Shooter on PS3 followed by Sports
+ Simulation only on 3DS, DS and Wii platforms


7. Multivariate non-graphical -- Quantitative
==============================================

Correlation plots

```{r, warning= FALSE, message= FALSE }

# Find correlation of quantitative variables
cor_plot <- video_games_data %>%
  mutate(Year = as.numeric(Year)) %>%
  select(NA_Sales, Global_Sales, Year)
cor(cor_plot) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped","hover"))

```

### Observations

+ NA_Sales and Global_Sales have 96.6% correlation. That means, Global gaming pattern is almost same as North America.  
+ Year is negatively correlated with both sales showing slow down in game sales.


8. Multivariate graphical code -- Quantitative
===============================================

Pairwise Plot

```{r}
# Correlation plot
pairs_plot <- video_games_data %>%
  mutate(Year = as.numeric(Year)) %>%
  select(NA_Sales, Global_Sales, Year)
pairs_plot %>%
  ggpairs()
```

### Observations

+ NA_Sales and Global_Sales have high positive correlation 0.966  
+ Correlation between Year and NA_Sales is -0.159 and Year and Global_Sales is -0.139. That means North America gaming slowing down faster than Global.

9. Multivariate non-graphical -- Categorical and Quantitative
=============================================================

matrix tables

```{r, warning= FALSE, message= FALSE }
video_games_data %>%
  group_by(Genre, Platform) %>%
  summarise(total_revenue = sum(NA_Sales)) %>%
  spread(Platform, total_revenue) %>%
  kable() %>%
  kable_styling()
```

### Observations

+ Shooter games on X360 (111.65) are the highest revenue earners. Action also highest on X360 (50.73) 
+ Least revenue on PSP (Platform 2.65) followed by PC (Role-playing 5 and Strategy 2.56)  
+ Adventure, Simulation, Strategy genres have least total revenues


```{r, warning= FALSE, message= FALSE }
video_games_data %>%
  group_by(Genre, Publisher) %>%
  summarise(total_revenue = sum(NA_Sales)) %>%
  spread(Genre, total_revenue) %>%
  kable() %>%
  kable_styling()
```

### Observations

+ Activision (109.84) has highest total revenues for Shooter games  
+ Take-Two Interactive (42.95) for Action genre  
+ Microsoft Game Studios highest revenue is from Shooter games (44.62)  
+ Nintendo's revenue is spread out in almost all genres. Highest in sports genre (75.27)  


10. Multivariate graphical -- Categorical and Quantitative
=============================================================

matrix group by and summarize quant graphs

```{r, warning= FALSE, message= FALSE }
# get total revenue by platform
video_games_data %>%
  group_by(Platform, Genre) %>%
  summarize (Revenue_sum = sum(NA_Sales)) %>%
  ggplot(aes(x = reorder(Platform, -Revenue_sum), y = Revenue_sum, fill = Genre)) +
  geom_bar(stat="identity", position="dodge") +
  coord_flip() +
  theme_classic() + 
  theme(axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.y = element_blank())

```


```{r, warning= FALSE, message= FALSE }
# get total revenue by platform
video_games_data %>%
  group_by(Platform, Genre) %>%
  summarize (Revenue_sum = sum(NA_Sales)) %>%
  filter(Revenue_sum >= 10.0) %>%
  ggplot(aes(x = reorder(Platform, -Revenue_sum), y = Revenue_sum, fill = Genre)) +
  geom_bar(stat="identity", position="dodge") +
  ggtitle("Platforms more than 10 Million total revenue", subtitle = "X360 has highest revenue and \nthe most genres above 10 Million") +
  coord_flip() +
  theme_classic() + 
  theme(axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.y = element_blank())

```



```{r, warning= FALSE, message= FALSE }
# get total revenue by platform
video_games_data %>%
  group_by(Publisher, Genre) %>%
  summarize (Revenue_sum = sum(NA_Sales)) %>%
  ggplot(aes(x = reorder(Publisher, -Revenue_sum), y = Revenue_sum, fill = Genre)) +
  geom_bar(stat="identity", position="dodge") +
  coord_flip() +
  theme_classic() + 
  theme(axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.y = element_blank())

```


```{r, warning= FALSE, message= FALSE }
# get total revenue by platform
video_games_data %>%
  group_by(Publisher, Genre) %>%
  summarize (Revenue_sum = sum(NA_Sales)) %>%
  filter(Revenue_sum >= 10.0) %>%
  ggplot(aes(x = reorder(Publisher, -Revenue_sum), y = Revenue_sum, fill = Genre)) +
  geom_bar(stat="identity", position="dodge") +
  ggtitle("Publishers above 10 Million in Revenue", subtitle = "Nintendo has most genres above 10 Million") +
  coord_flip() +
  theme_classic() + 
  theme(axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.y = element_blank())

```



```{r, include=FALSE}
# II) Statistical Analysis


#Questions for statistical analysis
#=========================================



#Multiple Linear regression
#================================

#Summary
#=======
```



Save Image of file
===================

```{r, warning= FALSE, message= FALSE }

# Save the rds file to reuse anything from this file in another file
save.image("TA.RData")
# recover using load()
# load("TA.RData")

```





